Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-09 paper.tex
Working on Experiments section
Improving the analysis of results and fixing some things

Next section provides a comparison between the feature reduction through SOM, and the feature selection techniques that have been described.

@@

Correlation coefficient, error measures and time to build the model have been 
computed for every method. Obtained results are presented in 
Figure \ref{fig:all_publishers_no_fs}
(detailed numeric results can be shown in Table Table \ref{tab:all_publishers_no_fs}
in the appendix of tables at the end of this paper).

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.4]{./imgs/prediction_all_publisher_all_features_Table3.eps}
\end{center}
\caption{Barplots showing the values obtained predicting \texttt{total\_sales}, including errorbars, with different regression methods (30 repetitions, 10-fold cross validation). All publishers and all the features have been considered.}
%This is not a boxplot - JJ
\label{fig:all_publishers_no_fs}
\end{figure*}

As far as the different methods are concerned, M5P model obtained the best results, 
both in time and error. The advantage of M5P is that it can learn and tackle 
regression tasks that have high dimensionality and categorical variables efficiently. 
Moreover, M5P generates reproducible and comprehensible representations that 
provide information on the decision process and does not require human intervention 
either for the operation or for interpretation. Thus, it is a very suitable model 
be incorporated in a publishing company processes (as we will show in 
Section \ref{subsec:decision_trees}).

@@

According to Figure \ref{fig:all_publishers_no_fs}, it can also be noticed that 
the Linear Regression model outperforms some other complex methods like the 
Random Forest, both in time and in obtained errors. 
%Although, Linear Regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.  % I change this sentence as its meaning is 'strange'...  [pedro]
Although, Linear Regression is considered as a simple model to build, it can obtain better results than more powerful models in comparable time.

kNN is the fastest method used in this study in terms of training time, as it 
is the simplest one. However, the model is slow when classifying large number of 
training examples, and it exhibits a poor generalisation ability since it does 
not learn anything from the training data.

@@

As a first conclusion, paying attention both to the cost in time to obtain the 
forecasting models and their accuracy, the M5P model would be the most adequate 
to solve the problem of how many books should be printed when a new book is 
published. This forecasting method, with these additional advantages, can be used 
for products with historical sales data and for new products with little or 
no historical data available.

@@

We have used both the {\tt CfsSubsetEval} \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:data_preproces}.

@@

After applying the feature selection process, we have run the same
forecasting models as in Section \ref{subsec:results_all_publishers}
for the whole dataset (all the publishers), but considering only the
selected features by each method. 
The results are shown in Figure \ref{fig:results_all_publishers_fs} 
(detailed numeric results can be shown in Table \ref{tab:results_all_publishers_fs}
in the appendix of tables at the end of this paper).
Examining the obtained results for each feature selection method, 
it can be seen that RFE got the best results compared to SOM and CSE. 
It can be noticed also that we obtain better performance using M5P, 
kNN and RF with the set of features selected by RFE than using all features. 
                                %Better publish results in
                                %the same table or refer to the table
                                %where it was published. Is this
                                %difference statistically significant?
                                %- JJ
As expected, in general, all feature selection methods have reduced the training 
time needed to build the forecasting methods. This is because they reduced the 
considered features and mainly because they excluded the categorical features, 
which are the hardest to be managed (they have many possible values). 
On the other side, CSE and SOM did not perform as good as RA. 
This could be explained due to the extensive reduction made by CSE and due to 
the `subjective' (but not so accurate) human intervention in the case of SOM.

@@

This section presents further experiments conducted on data concerning four 
specially interesting publishing company cases. These publishing companies were 
selected as representative cases which could be very interesting for decision 
makers and managers in the domain. The four cases are described as follows:

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_All.eps}
\end{center}
\caption{Barplots showing the values obtained predicting
  \texttt{total\_sales}, using all features, with different regression
  methods (30 repetitions, 10-fold cross validation). Results obtained
  for different special publishing companies: UDL929 (the best selling
  publishing company), UDLW12 (the median selling publishing company),
  UDL704 (highest number of different titles sold) and UDLU11 (medium
  number of different books sold). 
% Just the features selected by ReliefFAttributeEval method have been considered.
}
\label{fig:attributeAll}
\end{figure*}
% Antonio - CONCERN - The text and the results must be contrasted. If I'm not wrong, I remember that we decided to include here just the results obtained by ReliefFAttributeEval, since they were quite good (maybe the best). But there are plotted apparently the results for all the features. Anyway, in the text, it is said that the process is using all the features, then apply FS. But here just the results for all the features are shown. Why don't we show also the results for the corresponding sets of features selected by each FS method?
% Actually in the previous version there were several tables with these results than have been moved to the Appendix. I think we should include another figure fro them. They show important information. ;)
% we can discuss this point later this morning.
% The thing is that in this plot we are using all features!! (here, no feature selection method has been used)

\begin{itemize}
    \item Best seller publishing company: this case represents the publishing company that sells the highest number of copies regardless the title of the books sold. Therefore, it is an example of a case on a higher business scale.
    \item Mid-range seller publishing company: this represents a publishing company that sells medium number of copies compared to other publishing companies (Medium business scale). 
    \item Highest variation publishing company: this is an example of a publishing company that follows a strategy in publishing a very wide range of different titles.
    \item Medium varied publishing company: this case represents a publishing company that has a median rank between the other publishing companies regarding the variety of titles sold.
\end{itemize}

@@

Evaluation results of the obtained models (without performing any feature selection 
method) for the selected four cases  have been summarized in Figure \ref{fig:attributeAll} 
(detailed numeric results can be seen in Tables 
\ref{Table:case1results_no_fs}, \ref{Table:case2results_no_fs}, 
\ref{Table:case3results_no_fs} and \ref{Table:case4results_no_fs} 
in the appendix of tables at the end of this paper).
Results in this Figure show that the models performed similarly to the case of 
the global models for all publishers, which were previously presented in 
Table \ref{tab:all_publishers_no_fs}. 
In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR. 
In the case of Best selling publisher houses (i.e. UDL929) and publishers who 
publish wide range of different books (i.e. UDL704), M5P could be recommended 
as it shows more accurate forecasting results than the other models. 
While in the case of medium sized publishers, in terms of sales and number 
of published books, the RF model would be adequate.

@@

%  dejamos ésta finalmente: tablas al apéndice + incluimos nueva figura con los datos del RFE.
For clarity purpose, only obtained results after applying the RFE method for the 
four cases are shown in Figure \ref{fig:casesReliefFAttributeEval}
 (detailed numeric results can be shown in 
Tables \ref{Table:case1results_fs_rf}, \ref{Table:case2results_fs_rf}, 
\ref{Table:case3results_fs_rf} and \ref{Table:case4results_fs_rf}
in the appendix of tables at the end of this paper).
This one was chosen since the selected features by RFE method showed in the 
previous experiment the highest predictive power among all models.
As can be shown, RFE reduction has noticeably improved the performance of all 
classifiers specially in the case of the best selling publisher house (i.e. UDL929) 
and the publisher which publishes a wide range of different books (i.e. UDL704). 
For the rest of the results which are obtained by CSE and SOM feature selection 
methods we refer the reader to the appendix of tables at the end of this paper.

>>>>

These FS techniques have been applied in the following section, including a comparison between all of them.

@@

Correlation coefficient, error measures and time to build the model have been 
computed for every method. Obtained results are presented in 
Figure \ref{fig:all_publishers_no_fs}
(detailed numeric results can be seen in Table \ref{tab:all_publishers_no_fs}
in the appendix of tables at the end of this paper).

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.4]{./imgs/prediction_all_publisher_all_features_Table3.eps}
\end{center}
\caption{Barplots showing the values obtained predicting \texttt{total\_sales}, including errorbars, with different regression methods (30 repetitions, 10-fold cross validation). All publishers and all the features have been considered.}
% Antonio - Should we explain the meaning of the dot and the small lines in every barplot? I guess they are mean and standard deviation, aren't they?
\label{fig:all_publishers_no_fs}
\end{figure*}

As far as the different methods are concerned, M5P model obtained the best results, 
both in time and error. The advantage of M5P is that it can learn and tackle 
regression tasks that have high dimensionality and categorical variables efficiently. 
Moreover, M5P generates reproducible and comprehensible representations that 
provide information on the decision process and does not require human intervention 
either for the operation or for interpretation. Thus, it is a very suitable model to be incorporated in a publishing company processes (as we will show in 
Section \ref{subsec:decision_trees}).

@@

According to Figure \ref{fig:all_publishers_no_fs}, it can also be noticed that 
the Linear Regression model gets a better correlation value and some error measures than other complex methods like the Random Forest. 
%Although, Linear Regression is considered as a simple model to build, more powerful models can obtain better results in comparable time.  % I change this sentence as its meaning is 'strange'...  [pedro]
% Antonio - I have rewritten it. ;)
So even though Linear Regression is considered as a simple model to build, it can obtain better results than more powerful models in comparable time.

kNN is the fastest method used in this study in terms of training time, as it 
is the simplest one. However, the model is slow when classifying large number of 
training examples, and it exhibits a poor generalisation ability since it does 
not learn enough from the training data.

@@

MLP also gets a very good correlation coefficient, however it takes the largest time to built the models, and obtains high error measures. ELM shows a good balance, since it is very fast in the training phase (the second faster) and yields good results according to the correlation and the error metrics.

As a first conclusion, paying attention both to the cost in time to obtain the 
forecasting models and their accuracy, the M5P model would be the most adequate 
to solve the problem of how many books should be printed when a new book is 
published considering all the pre-sales data. Therefore this forecasting method, with these additional advantages, can be used for products with historical sales data and for new products with little or no historical data available.

@@

We have used both the {\tt CfsSubsetEval} (CSE) \cite{Hall1998} (a correlation-based feature subset evaluation method) and the ReliefFAttributeEval (RFE) \cite{RobnikSikonja1997} (an adaptation of relief for attribute estimation) evaluation methods, implemented in the Weka tool and described in Section \ref{subsec:data_preproces}.

@@

After applying the feature selection process, we have run the same
forecasting models as in Section \ref{subsec:results_all_publishers}
for the whole dataset (all the publishers), but considering only the
selected features by each method. 
The results are shown in Figure \ref{fig:results_all_publishers_fs} 
(numeric results are shown in Table \ref{tab:results_all_publishers_fs}
in the appendix of tables).
Examining the obtained results for each feature selection method, 
it can be seen that RFE got the best results in the comparison with SOM and CSE, both considering the quality/accuracy and also the standard deviation.
This could be explained due to the extensive reduction made by CSE and due to 
the `subjective' (but not so accurate) human intervention in the case of SOM. 
It can be noticed also that we obtain better results using M5P, kNN, and RF with the set of features selected by RFE than using all features, so the application of FS has improved their overall performance.

As expected, in general, all feature selection methods have reduced the training 
time needed to build the forecasting models, considerably in the most time expensive in previous experiment. This is because they reduced the 
considered features and mainly because they excluded the categorical features, 
which are the hardest to be managed (they have many possible values). 
On the other side, CSE and SOM did not perform as good as RFE.

@@

This section presents further experiments conducted on data concerning four 
specially relevant publishing company cases. These companies were 
selected as representative cases which could be very interesting for decision 
makers and managers in the domain. The four cases are described as follows:

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_All.eps}
\end{center}
\caption{Barplots showing the values obtained predicting
  \texttt{total\_sales}, using all features, with different regression
  methods (30 repetitions, 10-fold cross validation). Results obtained
  for different special publishing companies: UDL929 (the best selling
  publishing company), UDLW12 (the median selling publishing company),
  UDL704 (highest number of different titles sold) and UDLU11 (medium
  number of different books sold). 
}
\label{fig:attributeAll}
\end{figure*}

\begin{itemize}
    \item \textit{Best seller publishing company}: this case represents the publishing company that sells the highest number of copies regardless the title of the books sold. Therefore, it is an example of a case on a higher business scale.
    \item \textit{Mid-range seller publishing company}: this represents a publishing company that sells medium number of copies compared to other publishing companies (Medium business scale). 
    \item \textit{Highest variation publishing company}: this is an example of a publishing company that follows a strategy in publishing a very wide range of different titles.
    \item \textit{Medium varied publishing company}: this case represents a publishing company that has a median rank between the other publishing companies regarding the variety of titles sold.
\end{itemize}

@@

Evaluation results of the obtained models (without performing any feature selection method) for the selected four cases  have been summarized in Figure \ref{fig:attributeAll} 
(numeric results can be seen in Tables 
\ref{Table:case1results_no_fs}, \ref{Table:case2results_no_fs}, 
\ref{Table:case3results_no_fs} and \ref{Table:case4results_no_fs} 
in the appendix of tables).
Results in the figure show that the models performed similarly to the case of 
the global models for all publishers, which were previously presented in 
Figure \ref{fig:all_publishers_no_fs}. 
In general, M5P, RF and SVM performed better than the `simple' classifiers kNN and LR. 
In the case of Best selling publisher houses (i.e. UDL929) and publishers who 
publish wide range of different books (i.e. UDL704), M5P could be recommended 
as it shows more accurate forecasting results than the other models. 
While in the case of medium sized publishers, in terms of sales and number 
of published books, the RF model would be adequate.

@@

%  dejamos ésta finalmente: tablas al apéndice + incluimos nueva figura con los datos del RFE.
For clarity purpose, only obtained results after applying the RFE method for the 
four cases are shown in Figure \ref{fig:casesReliefFAttributeEval}
 (detailed numeric results can be seen in 
Tables \ref{Table:case1results_fs_rf}, \ref{Table:case2results_fs_rf}, 
\ref{Table:case3results_fs_rf} and \ref{Table:case4results_fs_rf}
in the appendix of tables).
This one was chosen since the selected features by RFE method showed in the 
previous experiment the highest predictive power among all models.
As can be shown, RFE reduction has noticeably improved the performance of all 
classifiers specially in the case of the best selling publisher house (i.e. UDL929) 
and the publisher which publishes a wide range of different books (i.e. UDL704). 
For the rest of the results which are obtained by CSE and SOM feature selection 
methods we refer the reader to the appendix of tables at the end of this paper.
